---
title: "Writing reproducible code in R"
output: html_notebook
---

Read Iris data into workspace

```{r}
library(RCurl)
iris <- read.csv(text=getURL("https://raw.githubusercontent.com/BES2016Workshop/reproduciblecodeR/master/iris.csv"))
```

Tidy up the iris data using the `gather()`, `separate()` and `spread()` functions. 

```{r}
library(tidyr)
iris_tidy <- gather(iris, species, value, -measurement) %>%
  separate(measurement, c("sample", "measurement"), sep="_") %>%
  spread(measurement, value)
```

Note that I have used the `%>%` pipe operator, which is explained in the 'Manipulating and summarising data' section. 

Summarise the data using `group_by()` `select()` and `summarise_each()` to get mean and sd of each measurement, grouped by species. 

```{r}
library(dplyr)
iris_summary <- group_by(iris_tidy, species) %>%
  select(-sample) %>% # we are not interested in sample
  summarise_each(c("mean", "sd"))
```

Using the `lm()` and `tidy()` functions, fit a linear model relating petal length to petal width and output the table of coefficients.

```{r}
lmfit <- lm(Petal.Length ~ Petal.Width, data = iris_tidy)
library(broom)
tidy(lmfit)
```

Use `ggplot()` to create a plot of the above linear model, coloured by species.

```{r}
library(ggplot2)
library(cowplot)

p <- ggplot(iris_tidy, aes(x = Petal.Width, y = Petal.Length, colour = species)) + 
  geom_point()

p
```

